Seminarium TI 3700\\ Data Analysis on Twitter: An Overview

### 2014-03-26 paper_final.tex
Intro 2.0

Microblogging has grown out to become one of the most interesting forms of social media. Its most popular implementation has to be Twitter, 
where users can share short messages, called tweets, with any other user. These short 140 character messages often contain valuable information about the user, their
interests, opinions, etc. This information can be very useful for a variety of applications, making social web data analytics an important field within
information technology. One of the biggest challenges is finding a way to extract the intended information from these tweets.

This paper is dedicated to giving an overview of successful techniques and useful applications of these social web data analytics. 
We will build up from the basic techniques used by developers to collect tweets, to effective techniques that extract useful information from them. 
In the first following section the Twitter API will be evaluated, which will show that the platform offers useful tools and commands to retrieve 
specific datasets, or even a completely random sample stream of tweets. Once Twitter's API has been evaluated, a first series of techniques will be introduced
that focus on the analysis of a single tweet. These techniques offer insight in how machines and algorithms are being used to infer meaning from a tweet.
However, certain applications require the analysis of a set of tweets instead of just a single one. The final chapter is therefore dedicated to the explanation\
of common techniques used to retrieve information from multiple tweets. The conclusion of this paper involves a quick summary of the techniques that
have been reviewed throughout this paper.

>>>>

In the age of smartphones and glorified self-interest certain platforms have grown out to become massive databases filled with human-produced information.
A very popular way of communicating is microblogging, where you share real-time short messages with everyone on the Internet. Today, the most succesful
microblogging platform is Twitter, where users share 140 character messages (tweets) with the rest of the world. These short 140 messages often contain 
valuable information about the user, their interests, opinions, etc. This information can be very useful for a variety of applications, 
making social web data analytics an important field within information technology. One of the biggest challenges is finding a way to extract the intended 
information from these tweets. This paper is a survey dedicated to giving an overview of successful techniques and useful applications of these social 
web data analytics. Our working method involved analysing the methods of how researchers do their research on Twitter data. The overall method that emerged 
were three distinct steps. The first step is the selection of data, in this case tweets, which can be done by using Twitters API. The second step was the 
extraction of meaningful information from this data. The extraction process showed two separate perspectives. The single tweet perspective, where you extract
information from a single tweet and its attributes, and the perspective of a set of tweets in which we look for a pattern. Both perspectives are separately
handled within this paper. The third and final step was the application of the extracted information, where entities were created that build upon extracted 
information.
This paper is written from the perspective of these three steps. We will build up from the basic techniques used by developers to collect tweets, to effective techniques that extract useful information from them. 
In the first following section the Twitter API will be evaluated, which will show that the platform offers useful tools and commands to retrieve 
specific datasets, or even a completely random sample stream of tweets. Once Twitter's API has been evaluated, a first series of techniques will be introduced
that focus on the analysis of a single tweet. These techniques offer insight in how machines and algorithms are being used to infer meaning from a tweet.
However, certain applications require the analysis of a set of tweets instead of just a single one. The final chapter is therefore dedicated to the explanation\
of common techniques used to retrieve information from multiple tweets. The conclusion of this paper involves a quick summary of the techniques that
have been reviewed throughout this paper.
